---
title: "p8105_hw5_ml4239"
author: "Man Luo"
date: "2018/11/7"
output: github_document
---

```{r setup, include = FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(grid)
library(httr)
library(knitr)
```

##P.1

###import and tidy data
```{r,message = FALSE}
data = 
  tibble(file_name = list.files(path = './data/P1')) %>% 
  mutate(name = map(.x = str_c("./data/P1/", file_name),~read_csv(.x))) %>% 
  unnest() %>% 
  separate(file_name, into = c("group", "id"), sep = "_",remove = F) %>% 
  gather(key = week, value = observation, week_1:week_8) %>% 
  mutate(week = str_replace(week, "week_", ""),
         file_name = str_replace(file_name, ".csv", ""),
         id = str_replace(id, ".csv", "")) 

data
```

###make a spaghetti
```{r,out.width = "80%"}
data %>% 
  ggplot(aes(x = week, y = observation, group = file_name, col = group))+
  geom_line() +
  labs(
    title = "Observations on Each Subject over Time",
    x = "Week",
    y = "Observation",
    caption = "Data from a longitudinal study") +
  theme(legend.position = "bottom")

```

**Comments**The control group has a lower observation data compared to experiment arm. Even thought control and experiment arms might have similar observations for the first several weeks, with the time goes, control group has a lower observations in the end.  


##P.2

###Describe the raw data.
```{r message=F}
homicide_data <- read_csv('./data/P2/homicide-data.csv') 

```
The raw data contains `r dim(homicide_data)` observations including `r nrow(homicide_data)` people with `r ncol(homicide_data)` variables. The variables includes:`r colnames(homicide_data)`


###Create a city_state variable & Summarize total_homicides, unsolved_homicides within cities
```{r}

homicide_data_city_state<-homicide_data %>%  
  mutate(city_state = str_c(city, ",", state)) 

  
homicide_num<-homicide_data_city_state %>%   
  group_by(city_state) %>%
  summarise( total_homicide = n(),
    unsolved_homicide = sum(disposition == "Closed without arrest" | disposition == "Open/No arrest")) 

homicide_num

```

###Estimate the proportion of homicides that are unsolved for the city of Baltimore, MD
```{r, message= FALSE}
homicide_num_MD =  homicide_num %>%
  filter(city_state == "Baltimore,MD")

  prop.test(homicide_num_MD$unsolved_homicide, homicide_num_MD$total_homicide) %>% 
    broom::tidy() %>% 
    select(estimate, conf.low, conf.high) %>% 
  knitr::kable()
  
```

###Prop.test for each of the cities
```{r,warning= FALSE}

prop_city = function(x, y){
  
  selection = prop.test(x,y) %>% 
    broom::tidy() %>% 
  select(estimate, conf.low, conf.high)
  
  selection
  
}

prop_city<-map2(.x = homicide_num$unsolved_homicide, .y = homicide_num$total_homicide, ~prop_city(.x, .y)) %>% 
  bind_rows() %>% 
  mutate(city_state = homicide_num$city_state) %>% 
  select(city_state, everything()) 

prop_city
```

###Create a plot that shows the estimates and CIs for each city

```{r}
prop_city %>% 
  ggplot(aes(x = reorder(city_state, estimate), y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 80, hjust = 1))+
  labs(
    title = "Estimates and CIs for Each City",
    x = "city, State",
    y = "Estimates",
    caption = "Data from the Washington Post")
```

